Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-15 paper/abstraction/appendix.tex
more edits

    \noindent
    Lemma 7 lets us conclude that there exists a node $n$ such that:

@@

\end{lem}
%
%
\para{Note:}
Lemma 10 tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
We use this fact to define the local preference function ($\Pref : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $\Pref(m) = \Pref(f(m))$ for all product graph nodes $m$. We do this to normalize policies so they refer to the exact same BGP local preferences. This is useful because we are proving syntactic equivalence of commutativity rather than semantic equivalence.
%
\begin{defn}
  Assign $\Pref(m) = \Pref^A(f_{pg}(m))$ as increasing integers starting from 0 according to the total ordering for $\leq$.
  From Lemma 10, we know that $\Pref$ and $\Pref^A$ preserve the total ordering since: $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$.
\end{defn}

\vspace{3em}
\subsection{Constraint Substitution (Part 2)}

@@

  Applying Lemma 10 with the fact that $f(\ell) = l = \Topo(M)$ this is equivalent to the following:

@@

  \vspace{.4em}
  \noindent
  \textbf{Case} ($t = \$x$)
  \vspace{.4em}

@@

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc = append_i \\
     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, l') \in \Gamma(x), \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \textbf{if } in = \{ G.start \} \text{ and } l'=\ell \textbf{ then } \bullet \\
     ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{else } \Pref^A(M) : (\Con(in, \ell, \Gamma, f, G),q_N) \rightarrow (\Con(out, \ell, \Gamma, f, G), q_M) ~] ~] ~]\\
  \end{array} \]%

  After filtering the cases where $in = \{ G.start \}$ and $l' \neq \ell$, we have the same situation as the previous case. 
  However, we know that each $PG_{i}$ was constructed from $con(r_{i}, \ell, \Gamma, f, G) \cap end(l_{i})$. This means that the only state in $PG_{i}$ connected to the start node ($\mathit{start}$) is a node for $l_{i}$. This was ensured by the fact that the transition function for each regular expression $\sigma_{i}(q_0,l) = q$ is defined only for locations $l \in L$ where $L = \{ l_{i} \}$ from the construction of the automata. We apply Lemma 10 with the fact that $f(\ell) = \Topo(M)$:

@@

\vspace{2em}
\begin{thm}
  For all \sysname policies $pol$, contexts $\Gamma$, topologies $G$ and $G^A$ related by homomorphism $f : G \rightarrow G^A$:
  $$\Con(\Compile(pol,G^A),\Gamma,f,G) = \Compile(\Con(pol,\Gamma,f),G)$$

@@

    \vspace{.5em}
    \noindent
    The proof simply uses Theorem 11 after rewriting the policy according to $\Con$ and $\Compile$.
    Given a policy $pol = p_1, \ldots, p_n$ we apply Theorem 11 after rewriting the policy. For the left side:
    \[
    \begin{array}{llll}
      & & \Con(\Compile(pol,G^A),\Gamma,f,G) \\
      &=& \Con(\Compile(p_1, \ldots, p_n, G^A),\Gamma,f,G) & \text{Substitution} \\
      &=& \Con(\CompileMbgp([\CompilePg(p_1, G^A), \ldots, \CompilePg(p_n, G^A)]),\Gamma,f,G)
            & \text{Definition of Compile} \\
      &=& \Con(\CompileMbgp([(t_1,PG^A_1,\Pref^A_1), \ldots, (t_n,PG^A_n,\Pref^A_n)]),\Gamma,f,G)
            & \text{Assumption}\\
    \end{array}
    \]

>>>>

    \noindent
    Lemma 8 lets us conclude that there exists a node $n$ such that:

@@

\end{lem}
%
%
\para{Note:}
Lemma 10 tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
We use this fact to define the local preference function ($\Pref : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $\Pref(m) = \Pref(f(m))$ for all product graph nodes $m$. We do this to normalize policies so they refer to the exact same BGP local preferences. This is useful because we are proving syntactic equivalence of commutativity rather than semantic equivalence.
%

\vspace{1em}
\begin{lem}
  For all node $m$, $\Pref(m) = \Pref^A(f_{pg}(m))$.
  \begin{proof}
    $\Pref$ and $\Pref^A$ assign values to PG nodes for each topology location as increasing integers starting from 0 according to the total ordering for $\leq$.
    From Lemma 10, we know that $\Pref$ and $\Pref^A$ preserve the total ordering since: $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$. Also, because there can only be a single product graph node for a particular location and set of states (since automata are determinized), and from Lemma 5 we know that for each $m$ there exists a node $f(m)$ with the same states it must be the case that $\Pref(m) = \Pref^A(f_{pg}(m))$
  \end{proof}
\end{lem}

\vspace{2em}
\subsection{Constraint Substitution (Part 2)}

@@

  Applying Lemma 12 with the fact that $f(\ell) = l = \Topo(M)$ this is equivalent to the following:

@@

  \vspace{2em}
  \noindent
  \textbf{Case} ($t = \$x$)
  \vspace{.4em}

@@

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc = append_i \\
     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, l') \in \Gamma(x), \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \text{if } in = \{ G.start \} \text{ and } l'=\ell \text{ then } \bullet \\
     ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \text{else } \Pref^A(M) : (\Con(in, \ell, \Gamma, f, G),q_N) \rightarrow (\Con(out, \ell, \Gamma, f, G), q_M) ~] ~] ~]\\
  \end{array} \]%

  After filtering the cases where $in = \{ G.start \}$ and $l' = \ell$, we have the same situation as the previous case. 
  However, we know that each $PG_{i}$ was constructed from $con(r_{i}, \ell, \Gamma, f, G) \cap end(l_{i})$. This means that the only state in $PG_{i}$ connected to the start node ($\mathit{start}$) is a node for $l_{i}$. This was ensured by the fact that the transition function for each regular expression $\sigma_{i}(q_0,l) = q$ is defined only for locations $l \in L$ where $L = \{ l_{i} \}$ from the construction of the automata. We apply Lemma 12 with the fact that $f(\ell) = \Topo(M)$:

@@

\vspace{2em}
\subsection{Substitution of Policies (Step 3)}

The final step is now to show the commutativity property for entire \sysname policies.

\begin{thm}
  For all \sysname policies $pol$, contexts $\Gamma$, topologies $G$ and $G^A$ related by homomorphism $f : G \rightarrow G^A$:
  $$\Con(\Compile(pol,G^A),\Gamma,f,G) = \Compile(\Con(pol,\Gamma,f),G)$$

@@

    \vspace{.5em}
    \noindent
    The proof simply uses Theorem 13 after rewriting the policy according to $\Con$ and $\Compile$.
    Given a policy $pol = p_1, \ldots, p_n$, we compute the left-hand side:
    \[
    \begin{array}{llll}
      & & \Con(\Compile(pol,G^A),\Gamma,f,G) \\
      &=& \Con(\Compile(p_1, \ldots, p_n, G^A),\Gamma,f,G) & \text{Substitution} \\
      &=& \Con(\CompileMbgp([\CompilePg(p_1, G^A), \ldots, \CompilePg(p_n, G^A)]),\Gamma,f,G)
            & \text{Definition of Compile} \\
      &=& \Con(\CompileMbgp([(t_1,PG^A_1,\Pref^A_1), \ldots, (t_n,PG^A_n,\Pref^A_n)]),\Gamma,f,G)
            & \text{Assumption}\\
    \end{array}
    \]
